### 2021-11-09 elsevier/appendix.Rmd
for Elsevier journals

---
output: pdf_document
---
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\setcounter{equation}{0}

Fig.\ref{fig:s2021} is in Supplementary materials.
```{r s2021, echo=FALSE, fig.cap='A plot in Supplementary Materials', out.width="80%", fig.align='center'}
knitr::include_graphics(here::here("results", "pictures", "2021.png"))
```

Table.\ref{tab:stable} is in Supplementary materials.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:stable}This table again")
```

Some random SAS code  
```
PROC MCMC 
	data=Data outpost=Dataoutput 
		nbi=1000000 
		nmc=1000000
		thin=10
		seed=1
		diag=all
		monitor=(p1 p2 cp I w); 
```

### 2021-11-09 elsevier/manuscript.Rmd
for Elsevier journals

---
title: Article Name
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliation: Some Institute of Technology
    footnote: 1
  - name: Bob Security
    email: bob@example.com
    affiliation: Another University
  - name: Cat Memes
    email: cat@example.com
    affiliation: Another University
    footnote: 2
  - name: Derek Zoolander
    email: derek@example.com
    affiliation: Some Institute of Technology
    footnote: 2
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
abstract: |
  This is the abstract.  
  1. what is the study about?  
  2. what problem does it address?  
  3. how did you conduct the research?  
  4. what were the main findings?  
  5. why is it important?

keywords: "keywordA, keywordB"
journal: "An awesome journal"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
#linenumbers: true
numbersections: true
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage{lineno}\linenumbers
csl: harmful-algae.csl
output:
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
    includes:  
      in_header: my_header.tex
linkcolor: blue
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(here)
library(kableExtra)
library(tidyverse)

data <- read.csv(here("data", "process", "newdata.csv"))
```

# Introduction {#intro}
1. general information
1. research gap
1. research aim

# Materials and methods {#method}
## Adding figures {#figure}
Add Fig. \ref{fig:boxplot} here.

```{r boxplot, echo=FALSE, fig.cap='A boxplot', out.height="50%", fig.align='center'}
knitr::include_graphics(here::here("results", "figures", "boxplot.pdf"))
```

If the caption is too long (fig.\ref{fig:2021}), use the [text-reference](https://bookdown.org/yihui/rmarkdown/bookdown-markdown.html#text-references). 
See the code in "elsevier/manuscript.Rmd" for more information.

(ref:longcaption) This is a very long caption
```{r 2021, echo=FALSE, fig.cap='(ref:longcaption)', out.width="50%", fig.align='center'}
knitr::include_graphics(here::here("results", "pictures", "2021.png"))
```

## Adding tables {#table}
```{r, echo=FALSE, warning=FALSE, message=FALSE}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```

## Adding equation {#equation}
1. The _variable_ \(x\) and the __function__ \(f(x)\)
1. The *variable* $x$ and the **function** $f(x)$
1. superscript^2^
1. NO~2~, NO~3~, PO~4~, NH~4~

\[Y|X \sim Bernoulli(p)\]

or

\begin{equation}
\label{eq:cutoff}
p(x) = P(Y = 1|X = x) = 
\left\{
    \begin{array}{lr}
          p_1 = P(Y = 1|X \le cp), & \text{if } x \le cp\\
          p_2 = P(Y = 1|X > cp), & \text{if } x > cp
    \end{array}
\right.
\end{equation}

## Cross-reference
* figure: `\ref{fig:label}`
* table: `\ref{tab:label}`
* equation: `\ref{eq:label}`
* section: `\ref{label}`

**Note:** only alphanumeric characters (`a-z`, `A-Z`, `0-9`), `-`, `/`, and `:` are allowed in labels.

1. Fig.\ref{fig:boxplot} and fig.\ref{fig:2021}
1. Table. \ref{tab:cooltable}
1. Equation \ref{eq:cutoff}
1. Section \ref{intro} and section \ref{figure}

## Citation syntax
- cite directly @Davis2009
- put citations in parentheses [@Walls2018]
- cite multiple entries [@Davis2009; @Walls2018]
- suppress the mention of the author [-@Liu2011a]

# Results and discussion {#result}
## Use code inline
The maximum tooth length is `r max(data$len)`.

## Random things
- download `.csl` file at [Zotero Style Repository](https://www.zotero.org/styles)
- *References* section is created at the end of the document by default. 
To put *References* section in a specific place (e.g. before Supplementary Materials):

```
# References
<div id="refs"></div>
# Supplementary Materials
```
- check spelling in rmarkdown: `F7`
- [word count addin](https://github.com/benmarwick/wordcountaddin)

# Conclusions {#conclusion}

# CRediT authorship contribution statement {#authorship .unnumbered}

# Data availability {#datasharing .unnumbered}

# Declaration of competing interest {#declaration .unnumbered}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

# Acknowledgements {#thanks .unnumbered}

# Supplementary materials {#appendix .unnumbered}
```{r, child="appendix.Rmd"}

```

# References {#references .unnumbered}

### 2021-11-09 elsevier/manuscript.tex
for Elsevier journals

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

  \journal{An awesome journal} % Sets Journal name

\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Article Name},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

% Pandoc citation processing

% Pandoc header
\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}
\usepackage{setspace}\doublespacing
\usepackage{lineno}\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\begin{frontmatter}

  \title{Article Name}
    \author[Some Institute of Technology]{Alice Anonymous\corref{1}}
   \ead{alice@example.com} 
    \author[Another University]{Bob Security}
   \ead{bob@example.com} 
    \author[Another University]{Cat Memes\corref{2}}
   \ead{cat@example.com} 
    \author[Some Institute of Technology]{Derek Zoolander\corref{2}}
   \ead{derek@example.com} 
      \address[Some Institute of Technology]{Department, Street, City, State, Zip}
    \address[Another University]{Department, Street, City, State, Zip}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

  \begin{abstract}
  This is the abstract.\\
  1. what is the study about?\\
  2. what problem does it address?\\
  3. how did you conduct the research?\\
  4. what were the main findings?\\
  5. why is it important?
  \end{abstract}
   \begin{keyword} keywordA, keywordB\end{keyword}
 \end{frontmatter}

\section{Introduction}\label{intro}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  general information
\item
  research gap
\item
  research aim
\end{enumerate}

\section{Materials and methods}\label{method}

\subsection{Adding figures}\label{figure}

Add Fig. \ref{fig:boxplot} here.

\begin{figure}

{\centering \includegraphics[height=0.5\textheight]{C:/Users/LY/Google Drive/Git/writing_journal_article_in_rmarkdown/results/figures/boxplot}

}

\caption{A boxplot}\label{fig:boxplot}
\end{figure}

If the caption is too long (fig.\ref{fig:2021}), use the
\href{https://bookdown.org/yihui/rmarkdown/bookdown-markdown.html\#text-references}{text-reference}.
See the code in ``elsevier/manuscript.Rmd'' for more information.

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth]{C:/Users/LY/Google Drive/Git/writing_journal_article_in_rmarkdown/results/pictures/2021}

}

\caption{This is a very long caption}\label{fig:2021}
\end{figure}

\subsection{Adding tables}\label{table}

\begin{longtable}[]{@{}cll@{}}
\caption{\label{tab:unnamed-chunk-2}\label{tab:cooltable}Mean and
Median}\tabularnewline
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endfirsthead
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endhead
OJ & 22.7 & 20.66333\tabularnewline
VC & 16.5 & 16.96333\tabularnewline
\bottomrule
\end{longtable}

\subsection{Adding equation}\label{equation}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The \emph{variable} \(x\) and the \textbf{function} \(f(x)\)
\item
  The \emph{variable} \(x\) and the \textbf{function} \(f(x)\)
\item
  superscript\textsuperscript{2}
\item
  NO\textsubscript{2}, NO\textsubscript{3}, PO\textsubscript{4},
  NH\textsubscript{4}
\end{enumerate}

\[Y|X \sim Bernoulli(p)\]

or

\begin{equation}
\label{eq:cutoff}
p(x) = P(Y = 1|X = x) = 
\left\{
    \begin{array}{lr}
          p_1 = P(Y = 1|X \le cp), & \text{if } x \le cp\\
          p_2 = P(Y = 1|X > cp), & \text{if } x > cp
    \end{array}
\right.
\end{equation}

\subsection{Cross-reference}\label{cross-reference}

\begin{itemize}
\tightlist
\item
  figure: \texttt{\textbackslash{}ref\{fig:label\}}
\item
  table: \texttt{\textbackslash{}ref\{tab:label\}}
\item
  equation: \texttt{\textbackslash{}ref\{eq:label\}}
\item
  section: \texttt{\textbackslash{}ref\{label\}}
\end{itemize}

\textbf{Note:} only alphanumeric characters (\texttt{a-z}, \texttt{A-Z},
\texttt{0-9}), \texttt{-}, \texttt{/}, and \texttt{:} are allowed in
labels.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Fig.\ref{fig:boxplot} and fig.\ref{fig:2021}
\item
  Table. \ref{tab:cooltable}
\item
  Equation \ref{eq:cutoff}
\item
  Section \ref{intro} and section \ref{figure}
\end{enumerate}

\subsection{Citation syntax}\label{citation-syntax}

\begin{itemize}
\tightlist
\item
  cite directly Davis et al. (2009)
\item
  put citations in parentheses (Walls et al., 2018)
\item
  cite multiple entries (Davis et al., 2009; Walls et al., 2018)
\item
  suppress the mention of the author (2011)
\end{itemize}

\section{Results and discussion}\label{result}

\subsection{Use code inline}\label{use-code-inline}

The maximum tooth length is 33.9.

\subsection{Random things}\label{random-things}

\begin{itemize}
\tightlist
\item
  download \texttt{.csl} file at
  \href{https://www.zotero.org/styles}{Zotero Style Repository}
\item
  \emph{References} section is created at the end of the document by
  default. To put \emph{References} section in a specific place
  (e.g.~before Supplementary Materials):
\end{itemize}

\begin{verbatim}
# References
<div id="refs"></div>
# Supplementary Materials
\end{verbatim}

\begin{itemize}
\tightlist
\item
  check spelling in rmarkdown: \texttt{F7}
\item
  \href{https://github.com/benmarwick/wordcountaddin}{word count addin}
\end{itemize}

\section{Conclusions}\label{conclusion}

\section*{CRediT authorship contribution statement}\label{authorship}
\addcontentsline{toc}{section}{CRediT authorship contribution statement}

\section*{Data availability}\label{datasharing}
\addcontentsline{toc}{section}{Data availability}

\section*{Declaration of competing interest}\label{declaration}
\addcontentsline{toc}{section}{Declaration of competing interest}

The authors declare that they have no known competing financial
interests or personal relationships that could have appeared to
influence the work reported in this paper.

\section*{Acknowledgements}\label{thanks}
\addcontentsline{toc}{section}{Acknowledgements}

\section*{Supplementary materials}\label{appendix}
\addcontentsline{toc}{section}{Supplementary materials}

\renewcommand{\thefigure}{S\arabic{figure}}

\setcounter{figure}{0} \renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0} \renewcommand{\theequation}{S\arabic{equation}}
\setcounter{equation}{0}

Fig.\ref{fig:s2021} is in Supplementary materials.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/LY/Google Drive/Git/writing_journal_article_in_rmarkdown/results/pictures/2021}

}

\caption{A plot in Supplementary Materials}\label{fig:s2021}
\end{figure}

Table.\ref{tab:stable} is in Supplementary materials.

\begin{longtable}[]{@{}cll@{}}
\caption{\label{tab:unnamed-chunk-4}\label{tab:stable}This table
again}\tabularnewline
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endfirsthead
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endhead
OJ & 22.7 & 20.66333\tabularnewline
VC & 16.5 & 16.96333\tabularnewline
\bottomrule
\end{longtable}

Some random SAS code

\begin{verbatim}
PROC MCMC 
    data=Data outpost=Dataoutput 
        nbi=1000000 
        nmc=1000000
        thin=10
        seed=1
        diag=all
        monitor=(p1 p2 cp I w); 
\end{verbatim}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-Davis2009}{}
Davis, T.W., Berry, D.L., Boyer, G.L., Gobler, C.J., 2009. The effects
of temperature and nutrients on the growth and dynamics of toxic and
non-toxic strains of Microcystis during cyanobacteria blooms. Harmful
Algae 8, 715--725. \url{https://doi.org/10.1016/j.hal.2009.02.004}

\hypertarget{ref-Liu2011a}{}
Liu, X., Lu, X., Chen, Y., 2011. The effects of temperature and nutrient
ratios on Microcystis blooms in Lake Taihu, China: An 11-year
investigation. Harmful Algae 10, 337--343.
\url{https://doi.org/10.1016/j.hal.2010.12.002}

\hypertarget{ref-Walls2018}{}
Walls, J.T., Wyatt, K.H., Doll, J.C., Rubenstein, E.M., Rober, A.R.,
2018. Hot and toxic: Temperature regulates microcystin release from
cyanobacteria. Science of the Total Environment 610-611, 786--795.
\url{https://doi.org/10.1016/j.scitotenv.2017.08.149}

\end{document}

### 2021-11-24 elsevier/appendix.Rmd
update `elsevier/`: revised YAML of manuscript.Rmd; add child documents: cover-letter, response-to-reviewer, credit, declaration of competing interest (.docx + .Rmd), acknowledgements, highlight

@@
 ---
-output: pdf_document
+output: 
+  bookdown::pdf_book: default
+  bookdown::word_document2: default  # for cross-references
 ---
@@
 \setcounter{equation}{0}
+
+# Supplementary materials {#appendix .unnumbered}
 
@@
           group_by(supp) %>%
-          summarise(median = median(len),
-                    mean = mean(len)) %>% 
+          summarise(median = round(median(len), 3),
+                    mean = round(mean(len), 3)) %>% 
 	kable("simple",

### 2021-11-24 elsevier/cover_letter.Rmd
update `elsevier/`: revised YAML of manuscript.Rmd; add child documents: cover-letter, response-to-reviewer, credit, declaration of competing interest (.docx + .Rmd), acknowledgements, highlight

---
output: 
  pdf_document: default
  bookdown::word_document2: default  # for cross-references
---
# Cover letter {-}

### New submission {-}
Month Day, Year

Dear Dr. AAA,

I am happy to submit my manuscript, **article_name**, for your consideration at *journal_name*. 
This work *do sth interesting*. 
The main conclusion is that *sth cool*.

All of the authors have read and approved the paper and it has not been published previously nor is it being considered by any other peer-reviewed journal.

The manuscript has also been submitted to bioRxiv as a preprint.

Sincerely,

Author_name, PhD  
Professor

### Resubmissions {-}
Month Day, Year

Dear Dr. BBB,

I am happy to resubmit my manuscript, **article_name**, for your reconsideration at *journal_name*. 
I am grateful to you and the reviewers who were very encouraging about the content of the manuscript.  
I apologize for taking so long to resubmit.  
Too many things got in the way over the past few months.

All of the authors have read and approved the paper and it has not been published previously nor is it being considered by any other peer-reviewed journal.

The manuscript was previously submitted to bioRxiv as a preprint.

Sincerely,

Author_name, PhD  
Professor

### 2021-11-24 elsevier/manuscript.Rmd
update `elsevier/`: revised YAML of manuscript.Rmd; add child documents: cover-letter, response-to-reviewer, credit, declaration of competing interest (.docx + .Rmd), acknowledgements, highlight

@@
 author:
-  - name: Alice Anonymous
-    email: alice@example.com
-    affiliation: Some Institute of Technology
+  - name: Author One
+    email: one@example.com
+    affiliation: a,1
+  - name: Author Two
+    email: two@example.com
+    affiliation: a,b
     footnote: 1
-  - name: Bob Security
-    email: bob@example.com
-    affiliation: Another University
-  - name: Cat Memes
-    email: cat@example.com
-    affiliation: Another University
+  - name: Author Three
+    email: three@example.com
+    affiliation: c
     footnote: 2
-  - name: Derek Zoolander
-    email: derek@example.com
-    affiliation: Some Institute of Technology
+  - name: Author Four
+    email: four@example.com
+    affiliation: a
     footnote: 2
 address:
-  - code: Some Institute of Technology
-    address: Department, Street, City, State, Zip
-  - code: Another University
-    address: Department, Street, City, State, Zip
+  - code: a
+    address: Graduate School of Engineering, Nagasaki University, 1-14 Bunkyo-machi, Nagasaki 852-8521, Japan
+  - code: b
+    address: Department, University, Street, City, State, Zip
+  - code: c
+    address: Department, University, Street, City, State, Zip
 footnote:
@@
     text: "Equal contribution"
+  - text: "^1^Present address: Department, University, Street, City, State, Zip"
 abstract: |
@@
 numbersections: true
-header-includes:
-    - \usepackage{setspace}\doublespacing
-    - \usepackage{lineno}\linenumbers
-csl: harmful-algae.csl
+layout: review      #review=doublespace, preprint=single, 5p=2column
+csl: harmful-algae.csl        #download .csl at www.zotero.org/styles
 output:
@@
       in_header: my_header.tex
+  bookdown::word_document2: default  # for cross-references
 linkcolor: blue
 ---
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+
 library(here)
+library(tidyverse)
 library(kableExtra)
-library(tidyverse)
+```
 
+```{r}
 data <- read.csv(here("data", "process", "newdata.csv"))
 ```
+
+\newpage
 
@@
 
-```{r boxplot, echo=FALSE, fig.cap='A boxplot', out.height="50%", fig.align='center'}
+```{r boxplot, fig.cap='A boxplot', out.height="50%", fig.align='center'}
 knitr::include_graphics(here::here("results", "figures", "boxplot.pdf"))
@@
 (ref:longcaption) This is a very long caption
-```{r 2021, echo=FALSE, fig.cap='(ref:longcaption)', out.width="50%", fig.align='center'}
+```{r 2021, fig.cap='(ref:longcaption)', out.width="50%", fig.align='center'}
 knitr::include_graphics(here::here("results", "pictures", "2021.png"))
@@
 ## Adding tables {#table}
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+```{r}
 data %>% 
@@
 
-# Results and discussion {#result}
+# Results {#result}
 ## Use code inline
@@
 
+# Discussion {#discussion}
+
 # Conclusions {#conclusion}
 
-# CRediT authorship contribution statement {#authorship .unnumbered}
+\newpage
 
-# Data availability {#datasharing .unnumbered}
+```{r, child="interest.Rmd"}
 
-# Declaration of competing interest {#declaration .unnumbered}
-The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+```
 
-# Acknowledgements {#thanks .unnumbered}
+```{r, child="credit.Rmd"}
 
-# Supplementary materials {#appendix .unnumbered}
+```
+
+```{r, child="thanks.Rmd"}
+
+```
+
+\newpage
+# References {#references .unnumbered}
+<div id="refs"></div>
+
+\newpage
 ```{r, child="appendix.Rmd"}
@@
 
-# References {#references .unnumbered}
+\newpage
+```{r, child="highlight.Rmd"}
+
+```
+
+# Graphical abstract {#graphic .unnumbered}
+Delete `eval=FALSE` before run the code chunk
+
+```{r, out.width="50%", fig.align='center', eval=FALSE}
+knitr::include_graphics(here("results", "figures", "graphical_abstract.pdf"))
+```
+
+\newpage
+```{r, child="cover_letter.Rmd"}
+
+```
+
+```{r, child="response_to_reviewers.Rmd"}
+
+```

### 2021-11-24 elsevier/manuscript.tex
update `elsevier/`: revised YAML of manuscript.Rmd; add child documents: cover-letter, response-to-reviewer, credit, declaration of competing interest (.docx + .Rmd), acknowledgements, highlight

@@
-\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+\documentclass[review]{elsarticle} %review=doublespace preprint=single 5p=2 column
 %%% Begin My package additions %%%%%%%%%%%%%%%%%%%
@@
 % Pandoc header
+%fix position of table, figure
 \usepackage{float}
@@
 }
-\usepackage{setspace}\doublespacing
-\usepackage{lineno}\linenumbers
 \usepackage{booktabs}
@@
   \title{Article Name}
-    \author[Some Institute of Technology]{Alice Anonymous\corref{1}}
-   \ead{alice@example.com} 
-    \author[Another University]{Bob Security}
-   \ead{bob@example.com} 
-    \author[Another University]{Cat Memes\corref{2}}
-   \ead{cat@example.com} 
-    \author[Some Institute of Technology]{Derek Zoolander\corref{2}}
-   \ead{derek@example.com} 
-      \address[Some Institute of Technology]{Department, Street, City, State, Zip}
-    \address[Another University]{Department, Street, City, State, Zip}
+    \author[a,1]{Author One}
+   \ead{one@example.com} 
+    \author[a,b]{Author Two\corref{1}}
+   \ead{two@example.com} 
+    \author[c]{Author Three\corref{2}}
+   \ead{three@example.com} 
+    \author[a]{Author Four\corref{2}}
+   \ead{four@example.com} 
+      \address[a]{Graduate School of Engineering, Nagasaki University, 1-14 Bunkyo-machi,
+Nagasaki 852-8521, Japan}
+    \address[b]{Department, University, Street, City, State, Zip}
+    \address[c]{Department, University, Street, City, State, Zip}
       \cortext[1]{Corresponding Author}
     \cortext[2]{Equal contribution}
+    \cortext[]{\textsuperscript{1}Present address: Department, University, Street,
+City, State, Zip}
 
@@
  \end{frontmatter}
+
+\newpage
 
@@
 
-\section{Results and discussion}\label{result}
+\section{Results}\label{result}
 
@@
 
+\section{Discussion}\label{discussion}
+
 \section{Conclusions}\label{conclusion}
 
-\section*{CRediT authorship contribution statement}\label{authorship}
-\addcontentsline{toc}{section}{CRediT authorship contribution statement}
+\newpage
 
-\section*{Data availability}\label{datasharing}
-\addcontentsline{toc}{section}{Data availability}
-
-\section*{Declaration of competing interest}\label{declaration}
+\section*{Declaration of competing interest}\label{interest}
 \addcontentsline{toc}{section}{Declaration of competing interest}
@@
 
+\section*{CRediT authorship contribution statement}\label{credit}
+\addcontentsline{toc}{section}{CRediT authorship contribution statement}
+
+\textbf{Author One:} Conceptualization, Methodology, Investigation, Data
+curation, Formal analysis, Visualization, Writing - Original Draft,
+Writing - review \& editing. \textbf{Author Two:} Supervision, Project
+administration, Funding acquisition, Conceptualization, Resources,
+Writing - Review \& Editing. \textbf{Author Three, Author Four:}
+Investigation.
+
+Further information
+\href{https://www.elsevier.com/authors/policies-and-guidelines/credit-author-statement}{here}.
+
 \section*{Acknowledgements}\label{thanks}
@@
 
-\section*{Supplementary materials}\label{appendix}
-\addcontentsline{toc}{section}{Supplementary materials}
+This work was supported by \ldots{}
 
-\renewcommand{\thefigure}{S\arabic{figure}}
-
-\setcounter{figure}{0} \renewcommand{\thetable}{S\arabic{table}}
-\setcounter{table}{0} \renewcommand{\theequation}{S\arabic{equation}}
-\setcounter{equation}{0}
-
-Fig.\ref{fig:s2021} is in Supplementary materials.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/LY/Google Drive/Git/writing_journal_article_in_rmarkdown/results/pictures/2021}
-
-}
-
-\caption{A plot in Supplementary Materials}\label{fig:s2021}
-\end{figure}
-
-Table.\ref{tab:stable} is in Supplementary materials.
-
-\begin{longtable}[]{@{}cll@{}}
-\caption{\label{tab:unnamed-chunk-4}\label{tab:stable}This table
-again}\tabularnewline
-\toprule
-Supplement type & Median & Mean\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-Supplement type & Median & Mean\tabularnewline
-\midrule
-\endhead
-OJ & 22.7 & 20.66333\tabularnewline
-VC & 16.5 & 16.96333\tabularnewline
-\bottomrule
-\end{longtable}
-
-Some random SAS code
-
-\begin{verbatim}
-PROC MCMC 
-    data=Data outpost=Dataoutput 
-        nbi=1000000 
-        nmc=1000000
-        thin=10
-        seed=1
-        diag=all
-        monitor=(p1 p2 cp I w); 
-\end{verbatim}
+\newpage
 
@@
 
+\newpage
+
+\renewcommand{\thefigure}{S\arabic{figure}}
+
+\setcounter{figure}{0} \renewcommand{\thetable}{S\arabic{table}}
+\setcounter{table}{0} \renewcommand{\theequation}{S\arabic{equation}}
+\setcounter{equation}{0}
+
+\section*{Supplementary materials}\label{appendix}
+\addcontentsline{toc}{section}{Supplementary materials}
+
+Fig.\ref{fig:s2021} is in Supplementary materials.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/LY/Google Drive/Git/writing_journal_article_in_rmarkdown/results/pictures/2021}
+
+}
+
+\caption{A plot in Supplementary Materials}\label{fig:s2021}
+\end{figure}
+
+Table.\ref{tab:stable} is in Supplementary materials.
+
+\begin{longtable}[]{@{}cll@{}}
+\caption{\label{tab:unnamed-chunk-11}\label{tab:stable}This table
+again}\tabularnewline
+\toprule
+Supplement type & Median & Mean\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Supplement type & Median & Mean\tabularnewline
+\midrule
+\endhead
+OJ & 22.7 & 20.663\tabularnewline
+VC & 16.5 & 16.963\tabularnewline
+\bottomrule
+\end{longtable}
+
+Some random SAS code
+
+\begin{verbatim}
+PROC MCMC 
+    data=Data outpost=Dataoutput 
+        nbi=1000000 
+        nmc=1000000
+        thin=10
+        seed=1
+        diag=all
+        monitor=(p1 p2 cp I w); 
+\end{verbatim}
+
+\newpage
+
+\section*{Highlights}\label{highlight}
+\addcontentsline{toc}{section}{Highlights}
+
+Short collection of bullet points: novel results + new methods\\
+- submitted: separate editable file -\textgreater{} online submission
+system.\\
+- file name: `Highlights'\\
+- 3 to 5 bullet points (maximum 85 characters, including spaces, per
+bullet point)
+
+\section*{Graphical abstract}\label{graphic}
+\addcontentsline{toc}{section}{Graphical abstract}
+
+Delete \texttt{eval=FALSE} before run the code chunk
+
+\newpage
+
+\section*{Cover letter}\label{cover-letter}
+\addcontentsline{toc}{section}{Cover letter}
+
+\subsubsection*{New submission}\label{new-submission}
+\addcontentsline{toc}{subsubsection}{New submission}
+
+Month Day, Year
+
+Dear Dr.~AAA,
+
+I am happy to submit my manuscript, \textbf{article\_name}, for your
+consideration at \emph{journal\_name}. This work \emph{do sth
+interesting}. The main conclusion is that \emph{sth cool}.
+
+All of the authors have read and approved the paper and it has not been
+published previously nor is it being considered by any other
+peer-reviewed journal.
+
+The manuscript has also been submitted to bioRxiv as a preprint.
+
+Sincerely,
+
+Author\_name, PhD\\
+Professor
+
+\subsubsection*{Resubmissions}\label{resubmissions}
+\addcontentsline{toc}{subsubsection}{Resubmissions}
+
+Month Day, Year
+
+Dear Dr.~BBB,
+
+I am happy to resubmit my manuscript, \textbf{article\_name}, for your
+reconsideration at \emph{journal\_name}. I am grateful to you and the
+reviewers who were very encouraging about the content of the
+manuscript.\\
+I apologize for taking so long to resubmit.\\
+Too many things got in the way over the past few months.
+
+All of the authors have read and approved the paper and it has not been
+published previously nor is it being considered by any other
+peer-reviewed journal.
+
+The manuscript was previously submitted to bioRxiv as a preprint.
+
+Sincerely,
+
+Author\_name, PhD\\
+Professor
+
+\section*{Response to reviewers}\label{response-to-reviewers}
+\addcontentsline{toc}{section}{Response to reviewers}
+
+\subsubsection*{Reviewer \#1 (Comments for the
+Author):}\label{reviewer-1-comments-for-the-author}
+\addcontentsline{toc}{subsubsection}{Reviewer \#1 (Comments for the
+Author):}
+
+\textbf{copy the comment of the reviewer here}
+
+\begin{quote}
+We have revised the sentence to the following: ``sth you revised''
+\end{quote}
+
+\subsubsection*{Reviewer \#2 (Comments for the
+Author):}\label{reviewer-2-comments-for-the-author}
+\addcontentsline{toc}{subsubsection}{Reviewer \#2 (Comments for the
+Author):}
+
+\textbf{copy the comment of the reviewer here}
+
+\begin{quote}
+Your response here
+\end{quote}
+
+A great example
+\href{https://github.com/SchlossLab/Tomkovich_PEG3350_mSphere_2021/blob/master/submission/response_to_reviewers.md}{here}.
+
 \end{document}

### 2022-02-11 elsevier/appendix.Rmd
Formatting Appendix

@@
 ---
-\renewcommand{\thefigure}{S\arabic{figure}}
+```{r setappendix, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+
+library(here)
+library(tidyverse)
+library(kableExtra)
+```
+
+# (APPENDIX) Appendix {-}
+
+\renewcommand{\thefigure}{A.\arabic{figure}}
 \setcounter{figure}{0}
-\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thetable}{A.\arabic{table}}
 \setcounter{table}{0}
-\renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\theequation}{A.\arabic{equation}}
 \setcounter{equation}{0}
 
-# Supplementary materials {#appendix .unnumbered}
+# Supplementary materials A {#appendixA}
+## A cool figure
 
 Fig.\ref{fig:s2021} is in Supplementary materials.
+
 ```{r s2021, echo=FALSE, fig.cap='A plot in Supplementary Materials', out.width="80%", fig.align='center'}
@@
 
+## An awesome table
 Table.\ref{tab:stable} is in Supplementary materials.
+
 ```{r, echo=FALSE, warning=FALSE, message=FALSE}
@@
 
+\newpage
+
+\renewcommand{\thefigure}{B.\arabic{figure}}
+\setcounter{figure}{0}
+\renewcommand{\thetable}{B.\arabic{table}}
+\setcounter{table}{0}
+\renewcommand{\theequation}{B.\arabic{equation}}
+\setcounter{equation}{0}
+
+# Supplementary materials B {#appendixB}
+## Some random code
+
 Some random SAS code  
@@
 ```
+
+## A green photo
+
+```{r green, echo=FALSE, fig.cap='A green photo', out.width="80%", fig.align='center'}
+knitr::include_graphics(here::here("results", "pictures", "green.jpeg"))
+```

### 2022-06-21 elsevier/manuscript.Rmd
`options(scipen=999)`: displaying `20000` instead of `2 x 10^4`
`!` update `manuscript`: add syntax before the output

@@
 library(kableExtra)
+
+options(scipen = 999)
 ```
@@
 # Introduction {#intro}
+
+Setting __global options__ that apply to every chunk in the file.
+
+````markdown
+`r ''````{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+
+library(here)
+library(tidyverse)
+library(kableExtra)
+
+# displaying 20000 instead of 2 x 10^4
+options(scipen = 999)
+```
+````
+
+````markdown
+`r ''````{r}
+# import data
+data <- read_csv(here("data", "process", "newdata.csv"))
+```
+````
+
+Ordered list items:
+
+```markdown
+1. general information
+1. research gap
+1. research aim
+```
+
+The output is:
+
 1. general information
@@
 
+````markdown
+`r ''````{r boxplot, fig.cap='A boxplot', out.height="50%", fig.align='center'}
+knitr::include_graphics(here::here("results", "figures", "boxplot.pdf"))
+```
+````
+
 ```{r boxplot, fig.cap='A boxplot', out.height="50%", fig.align='center'}
@@
 
-If the caption is too long (fig.\ref{fig:2021}), use the [text-reference](https://bookdown.org/yihui/rmarkdown/bookdown-markdown.html#text-references). 
-See the code in "elsevier/manuscript.Rmd" for more information.
+If the caption is too long (Fig. \ref{fig:2021}), use [text-reference](https://bookdown.org/yihui/rmarkdown/bookdown-markdown.html#text-references).
+
+`(ref:longcaption) This is a very long caption`
+
+````markdown
+`r ''````{r 2021, fig.cap='(ref:longcaption', out.width="50%", fig.align='center'}
+knitr::include_graphics(here::here("results", "pictures", "2021.png"))
+```
+````
 
@@
 ## Adding tables {#table}
+
+````markdown
+`r ''````{r}
+data %>% 
+          group_by(supp) %>%
+          summarise(median = median(len),
+                    mean = mean(len)) %>% 
+	kable("simple",
+	      booktabs = T,
+	      col.names = c("Supplement type", 
+	      	    	"Median",
+	      	    	"Mean"), 
+	      align = "cll",
+	      caption = "\\label{tab:cooltable}Mean and Median")
+```
+````
+
 ```{r}
@@
 ## Adding equation {#equation}
+
+```markdown
 1. The _variable_ \(x\) and the __function__ \(f(x)\)
@@
 1. NO~2~, NO~3~, PO~4~, NH~4~
+1. 25 µL
+```
+
+The output is:
+
+1. The _variable_ \(x\) and the __function__ \(f(x)\)
+1. The *variable* $x$ and the **function** $f(x)$
+1. superscript^2^
+1. NO~2~, NO~3~, PO~4~, NH~4~
+1. 25 µL
+
+Adding equations using the LaTeX syntax
+
+```latex
+\[Y|X \sim Bernoulli(p)\]
+```
 
@@
 
-or
+```latex
+\begin{equation}
+\label{eq:cutoff}
+p(x) = P(Y = 1|X = x) = 
+\left\{
+    \begin{array}{lr}
+          p_1 = P(Y = 1|X \le cp), & \text{if } x \le cp\\
+          p_2 = P(Y = 1|X > cp), & \text{if } x > cp
+    \end{array}
+\right.
+\end{equation}
+```
 
@@
 
+```latex
+\begin{subequations}
+  \label{eq:model}
+  \begin{align}
+  \label{eq:modela}
+P(y|\theta, \lambda) = 
+\left\{
+    \begin{array}{lr}
+       \theta & \text{if } y = 0\\
+       (1 - \theta) \frac{Poisson(y|\lambda)}{1 - PoissonCDF(0|\lambda)} 
+       & \text{if } y > 0
+    \end{array}
+\right. \\
+  \label{eq:modelb}
+logit(\theta) = \alpha_0 + \alpha_1 * x_1 + \alpha_2 * x_2 \\
+  \label{eq:modelc}
+log(\lambda) = \beta_0 + \beta_1 * x_1 + \beta_2 * x_2 + \nu
+  \end{align}
+\end{subequations}
+```
+
+\begin{subequations}
+  \label{eq:model}
+  \begin{align}
+  \label{eq:modela}
+P(y|\theta, \lambda) = 
+\left\{
+    \begin{array}{lr}
+          \theta & \text{if } y = 0\\
+          (1 - \theta) \frac{Poisson(y|\lambda)}{1 - PoissonCDF(0|\lambda)} 
+          & \text{if } y > 0
+    \end{array}
+\right. \\
+  \label{eq:modelb}
+logit(\theta) = \alpha_0 + \alpha_1 * x_1 + \alpha_2 * x_2 \\
+  \label{eq:modelc}
+log(\lambda) = \beta_0 + \beta_1 * x_1 + \beta_2 * x_2 + \nu
+  \end{align}
+\end{subequations}
+
 ## Cross-reference
@@
 
+```markdown
 1. Fig.\ref{fig:boxplot} and fig.\ref{fig:2021}
 1. Table. \ref{tab:cooltable}
-1. Equation \ref{eq:cutoff}
+1. Equation \ref{eq:cutoff}, Eq. \ref{eq:model}, Eq. \ref{eq:modela}
+1. Section \ref{intro} and section \ref{figure}
+```
+
+The output is:
+
+1. Fig. \ref{fig:boxplot} and Fig. \ref{fig:2021}
+1. Table. \ref{tab:cooltable}
+1. Equation \ref{eq:cutoff}, Eq. \ref{eq:model}, Eq. \ref{eq:modela}
 1. Section \ref{intro} and section \ref{figure}
@@
 ## Citation syntax
-- cite directly @Davis2009
-- put citations in parentheses [@Walls2018]
-- cite multiple entries [@Davis2009; @Walls2018]
-- suppress the mention of the author [-@Liu2011a]
+- `@Davis2009`: cite directly @Davis2009
+- `[@Walls2018]`: put citations in parentheses [@Walls2018]
+- `[@Davis2009; @Walls2018]`: cite multiple entries [@Davis2009; @Walls2018]
+- `[-@Liu2011a]`: suppress the mention of the author [-@Liu2011a]
 
@@
 ## Use code inline
+
+```markdown
+The maximum tooth length is `r '\x60r max(data$len)\x60'`.
+```
+
 The maximum tooth length is `r max(data$len)`.
@@
 
-```
+```markdown
 # References
@@
 ```
+
 - check spelling in rmarkdown: `F7`

### 2022-06-21 elsevier/manuscript.tex
`options(scipen=999)`: displaying `20000` instead of `2 x 10^4`
`!` update `manuscript`: add syntax before the output

@@
 \bibliographystyle{elsarticle-harv}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
 \usepackage{longtable,booktabs,array}
@@
 % Pandoc header
+% nullify the abstract environment
+% \renewenvironment{abstract}{}{}
+
+% Use the `align` environment inside the `subequations` environment 
+% from the `amsmath` package to label equation with subnumber (e.g. 1a, 1b)
+\usepackage{amsmath}
+
 %fix position of table, figure
@@
 
+Setting \textbf{global options} that apply to every chunk in the file.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{```\{r setup, include=FALSE\}}
+\NormalTok{knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)}
+
+\NormalTok{library(here)}
+\NormalTok{library(tidyverse)}
+\NormalTok{library(kableExtra)}
+
+\FunctionTok{# displaying 20000 instead of 2 x 10^4}
+\NormalTok{options(scipen = 999)}
+\NormalTok{```}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{```\{r\}}
+\FunctionTok{# import data}
+\NormalTok{data <- read_csv(here("data", "process", "newdata.csv"))}
+\NormalTok{```}
+\end{Highlighting}
+\end{Shaded}
+
+Ordered list items:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{1. }\FloatTok{general information}
+\FloatTok{1. research gap}
+\FloatTok{1. research aim}
+\end{Highlighting}
+\end{Shaded}
+
+The output is:
+
 \begin{enumerate}
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{```\{r boxplot, fig.cap='A boxplot', out.height="50%", fig.align='center'\}}
+\NormalTok{knitr::include_graphics(here::here("results", "figures", "boxplot.pdf"))}
+\NormalTok{```}
+\end{Highlighting}
+\end{Shaded}
+
 \begin{figure}
@@
 
-If the caption is too long (fig.\ref{fig:2021}), use the
+If the caption is too long (Fig. \ref{fig:2021}), use
 \href{https://bookdown.org/yihui/rmarkdown/bookdown-markdown.html\#text-references}{text-reference}.
-See the code in ``elsevier/manuscript.Rmd'' for more information.
+
+\texttt{(ref:longcaption)\ This\ is\ a\ very\ long\ caption}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{```\{r 2021, fig.cap='(ref:longcaption', out.width="50%", fig.align='center'\}}
+\NormalTok{knitr::include_graphics(here::here("results", "pictures", "2021.png"))}
+\NormalTok{```}
+\end{Highlighting}
+\end{Shaded}
 
@@
 \subsection{Adding tables}\label{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{```\{r\}}
+\NormalTok{data %>% }
+\BaseNTok{          group_by(supp) %>%}
+\BaseNTok{          summarise(median = median(len),}
+\BaseNTok{                    mean = mean(len)) %>% }
+\BaseNTok{    kable("simple",}
+\BaseNTok{          booktabs = T,}
+\BaseNTok{          col.names = c("Supplement type", }
+\BaseNTok{                    "Median",}
+\BaseNTok{                    "Mean"), }
+\BaseNTok{          align = "cll",}
+\BaseNTok{          caption = "\textbackslash{}\textbackslash{}label\{tab:cooltable\}Mean and Median")}
+\NormalTok{```}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{1. }\FloatTok{The _variable_ \textbackslash{}(x\textbackslash{}) and the __function__ \textbackslash{}(f(x)\textbackslash{})}
+\FloatTok{1. The *variable* $x$ and the **function** $f(x)$}
+\FloatTok{1. superscript^2^}
+\FloatTok{1. NO~2~, NO~3~, PO~4~, NH~4~}
+\FloatTok{1. 25 µL}
+\end{Highlighting}
+\end{Shaded}
+
+The output is:
+
 \begin{enumerate}
@@
   NH\textsubscript{4}
+\item
+  25 µL
 \end{enumerate}
+
+Adding equations using the LaTeX syntax
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\SpecialStringTok{\textbackslash{}[Y|X }\SpecialCharTok{\textbackslash{}sim}\SpecialStringTok{ Bernoulli(p)\textbackslash{}]}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-or
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{equation}\NormalTok{\}}
+\SpecialCharTok{\textbackslash{}label}\SpecialStringTok{\{eq:cutoff\}}
+\SpecialStringTok{p(x) = P(Y = 1|X = x) = }
+\SpecialCharTok{\textbackslash{}left\textbackslash{}\{}
+\SpecialStringTok{    }\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{array}\NormalTok{\}}\SpecialStringTok{\{lr\}}
+\SpecialStringTok{          p_1 = P(Y = 1|X }\SpecialCharTok{\textbackslash{}le}\SpecialStringTok{ cp), & }\SpecialCharTok{\textbackslash{}text}\NormalTok{\{if \}}\SpecialStringTok{ x }\SpecialCharTok{\textbackslash{}le}\SpecialStringTok{ cp}\SpecialCharTok{\textbackslash{}\textbackslash{}}
+\SpecialStringTok{          p_2 = P(Y = 1|X > cp), & }\SpecialCharTok{\textbackslash{}text}\NormalTok{\{if \}}\SpecialStringTok{ x > cp}
+\SpecialStringTok{    }\KeywordTok{\textbackslash{}end}\NormalTok{\{}\SpecialStringTok{array\}}
+\SpecialCharTok{\textbackslash{}right}\SpecialStringTok{.}
+\KeywordTok{\textbackslash{}end}\NormalTok{\{}\ExtensionTok{equation}\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
 
@@
 \end{equation}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{subequations}\NormalTok{\}}
+  \KeywordTok{\textbackslash{}label}\NormalTok{\{}\ExtensionTok{eq:model}\NormalTok{\}}
+  \KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{align}\NormalTok{\}}
+\SpecialStringTok{  }\SpecialCharTok{\textbackslash{}label}\SpecialStringTok{\{eq:modela\}}
+\SpecialStringTok{P(y|}\SpecialCharTok{\textbackslash{}theta}\SpecialStringTok{, }\SpecialCharTok{\textbackslash{}lambda}\SpecialStringTok{) = }
+\SpecialCharTok{\textbackslash{}left\textbackslash{}\{}
+\SpecialStringTok{    }\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{array}\NormalTok{\}}\SpecialStringTok{\{lr\}}
+\SpecialStringTok{       }\SpecialCharTok{\textbackslash{}theta}\SpecialStringTok{ & }\SpecialCharTok{\textbackslash{}text}\NormalTok{\{if \}}\SpecialStringTok{ y = 0}\SpecialCharTok{\textbackslash{}\textbackslash{}}
+\SpecialStringTok{       (1 - }\SpecialCharTok{\textbackslash{}theta}\SpecialStringTok{) }\SpecialCharTok{\textbackslash{}frac}\SpecialStringTok{\{Poisson(y|}\SpecialCharTok{\textbackslash{}lambda}\SpecialStringTok{)\}\{1 - PoissonCDF(0|}\SpecialCharTok{\textbackslash{}lambda}\SpecialStringTok{)\} }
+\SpecialStringTok{       & }\SpecialCharTok{\textbackslash{}text}\NormalTok{\{if \}}\SpecialStringTok{ y > 0}
+\SpecialStringTok{    }\KeywordTok{\textbackslash{}end}\NormalTok{\{}\SpecialStringTok{array\}}
+\SpecialCharTok{\textbackslash{}right}\SpecialStringTok{. }\SpecialCharTok{\textbackslash{}\textbackslash{}}
+\SpecialStringTok{  }\SpecialCharTok{\textbackslash{}label}\SpecialStringTok{\{eq:modelb\}}
+\SpecialStringTok{logit(}\SpecialCharTok{\textbackslash{}theta}\SpecialStringTok{) = }\SpecialCharTok{\textbackslash{}alpha}\SpecialStringTok{_0 + }\SpecialCharTok{\textbackslash{}alpha}\SpecialStringTok{_1 * x_1 + }\SpecialCharTok{\textbackslash{}alpha}\SpecialStringTok{_2 * x_2 }\SpecialCharTok{\textbackslash{}\textbackslash{}}
+\SpecialStringTok{  }\SpecialCharTok{\textbackslash{}label}\SpecialStringTok{\{eq:modelc\}}
+\SpecialStringTok{log(}\SpecialCharTok{\textbackslash{}lambda}\SpecialStringTok{) = }\SpecialCharTok{\textbackslash{}beta}\SpecialStringTok{_0 + }\SpecialCharTok{\textbackslash{}beta}\SpecialStringTok{_1 * x_1 + }\SpecialCharTok{\textbackslash{}beta}\SpecialStringTok{_2 * x_2 + }\SpecialCharTok{\textbackslash{}nu}
+\SpecialStringTok{  }\KeywordTok{\textbackslash{}end}\NormalTok{\{}\ExtensionTok{align}\NormalTok{\}}
+\KeywordTok{\textbackslash{}end}\NormalTok{\{}\ExtensionTok{subequations}\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{subequations}
+  \label{eq:model}
+  \begin{align}
+  \label{eq:modela}
+P(y|\theta, \lambda) = 
+\left\{
+    \begin{array}{lr}
+          \theta & \text{if } y = 0\\
+          (1 - \theta) \frac{Poisson(y|\lambda)}{1 - PoissonCDF(0|\lambda)} 
+          & \text{if } y > 0
+    \end{array}
+\right. \\
+  \label{eq:modelb}
+logit(\theta) = \alpha_0 + \alpha_1 * x_1 + \alpha_2 * x_2 \\
+  \label{eq:modelc}
+log(\lambda) = \beta_0 + \beta_1 * x_1 + \beta_2 * x_2 + \nu
+  \end{align}
+\end{subequations}
 
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{1. }\FloatTok{Fig.\textbackslash{}ref\{fig:boxplot\} and fig.\textbackslash{}ref\{fig:2021\}}
+\FloatTok{1. Table. \textbackslash{}ref\{tab:cooltable\}}
+\FloatTok{1. Equation \textbackslash{}ref\{eq:cutoff\}, Eq. \textbackslash{}ref\{eq:model\}, Eq. \textbackslash{}ref\{eq:modela\}}
+\FloatTok{1. Section \textbackslash{}ref\{intro\} and section \textbackslash{}ref\{figure\}}
+\end{Highlighting}
+\end{Shaded}
+
+The output is:
+
 \begin{enumerate}
@@
 \item
-  Fig.\ref{fig:boxplot} and fig.\ref{fig:2021}
+  Fig. \ref{fig:boxplot} and Fig. \ref{fig:2021}
 \item
@@
 \item
-  Equation \ref{eq:cutoff}
+  Equation \ref{eq:cutoff}, Eq. \ref{eq:model}, Eq. \ref{eq:modela}
 \item
@@
 \item
-  cite directly Davis et al. (2009)
+  \texttt{@Davis2009}: cite directly Davis et al. (2009)
 \item
-  put citations in parentheses (Walls et al., 2018)
+  \texttt{{[}@Walls2018{]}}: put citations in parentheses (Walls et al.,
+  2018)
 \item
-  cite multiple entries (Davis et al., 2009; Walls et al., 2018)
+  \texttt{{[}@Davis2009;\ @Walls2018{]}}: cite multiple entries (Davis
+  et al., 2009; Walls et al., 2018)
 \item
-  suppress the mention of the author (2011)
+  \texttt{{[}-@Liu2011a{]}}: suppress the mention of the author (2011)
 \end{itemize}
@@
 \subsection{Use code inline}\label{use-code-inline}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{The maximum tooth length is }\BaseNTok{`r max(data$len)`}\NormalTok{.}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-\begin{verbatim}
-# References
-<div id="refs"></div>
-# Supplementary Materials
-\end{verbatim}
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{# References}
+\NormalTok{<div id="refs"></div>}
+\FunctionTok{# Supplementary Materials}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-\renewcommand{\thefigure}{S\arabic{figure}}
+\appendix
 
-\setcounter{figure}{0} \renewcommand{\thetable}{S\arabic{table}}
-\setcounter{table}{0} \renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thefigure}{A.\arabic{figure}}
+
+\setcounter{figure}{0} \renewcommand{\thetable}{A.\arabic{table}}
+\setcounter{table}{0} \renewcommand{\theequation}{A.\arabic{equation}}
 \setcounter{equation}{0}
 
-\section*{Supplementary materials}\label{appendix}
-\addcontentsline{toc}{section}{Supplementary materials}
+\section{Supplementary materials A}\label{appendixA}
+
+\subsection{A cool figure}\label{a-cool-figure}
 
@@
 \end{figure}
+
+\subsection{An awesome table}\label{an-awesome-table}
 
@@
 
+\newpage
+
+\renewcommand{\thefigure}{B.\arabic{figure}}
+
+\setcounter{figure}{0} \renewcommand{\thetable}{B.\arabic{table}}
+\setcounter{table}{0} \renewcommand{\theequation}{B.\arabic{equation}}
+\setcounter{equation}{0}
+
+\section{Supplementary materials B}\label{appendixB}
+
+\subsection{Some random code}\label{some-random-code}
+
 Some random SAS code
@@
 \end{verbatim}
+
+\subsection{A green photo}\label{a-green-photo}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/LY/Google Drive/Git/writing_journal_article_in_rmarkdown/results/pictures/green}
+
+}
+
+\caption{A green photo}\label{fig:green}
+\end{figure}
 
@@
 I am happy to submit my manuscript, \textbf{article\_name}, for your
-consideration at \emph{journal\_name}. This work \emph{do sth
+consideration at \emph{journal\_name}. This work \emph{did sth
 interesting}. The main conclusion is that \emph{sth cool}.

### 2022-09-27 elsevier/manuscript.Rmd
add table with LaTeX math symbols

@@
 ````markdown
-`r ''````{r}
+`r ''````{r table1}
 data %>% 
@@
                     mean = mean(len)) %>% 
-	kable("simple",
+	kable("latex",
 	      booktabs = T,
@@
 	      caption = "\\label{tab:cooltable}Mean and Median")
+```
+
+````markdown
+`r ''````{r table2}
+para = c("Intercept ($\\beta_0$)",
+         "Parameter 1 ($\\beta_1$)",
+         "Parameter 2 ($\\beta_2$)",
+         "Hurdle probability ($\\theta$)")
+
+tab <- data.frame(
+	Parameter = para,
+	Estimate = c(1.6, 1.2, 6.2, 0.5),
+	Error = c(0.41, 0.02, 0.09, 0.07),
+	CI = c("[0.698, 2.477]",
+	       "[1.123, 1.235]",
+	       "[6.051, 6.423]",
+	       "[0.353, 0.644]"),
+	Rhat = c(rep("1.00", 4)))
+
+kable(tab,
+      "latex",
+      align = "lcccc",
+      booktabs = TRUE,
+      escape = FALSE,
+      caption = "\\label{tab:mathtable}A table with LaTeX Math symbols")
+```
+````
+
+```{r}
+para = c("Intercept ($\\beta_0$)",
+         "Parameter 1 ($\\beta_1$)",
+         "Parameter 2 ($\\beta_2$)",
+         "Hurdle probability ($\\theta$)")
+
+tab <- data.frame(
+	Parameter = para,
+	Estimate = c(1.6, 1.2, 6.2, 0.5),
+	Error = c(0.41, 0.02, 0.09, 0.07),
+	CI = c("[0.698, 2.477]",
+	       "[1.123, 1.235]",
+	       "[6.051, 6.423]",
+	       "[0.353, 0.644]"),
+	Rhat = c(rep("1.00", 4)))
+
+kable(tab,
+      "latex",
+      align = "lcccc",
+      booktabs = TRUE,
+      escape = FALSE,
+      caption = "\\label{tab:mathtable}A table with LaTeX Math symbols")
 ```

### 2022-09-27 elsevier/manuscript.tex
add table with LaTeX math symbols

@@
 \begin{Highlighting}[]
-\NormalTok{```\{r\}}
+\NormalTok{```\{r table1\}}
 \NormalTok{data %>% }
@@
 \BaseNTok{                    mean = mean(len)) %>% }
-\BaseNTok{    kable("simple",}
+\BaseNTok{    kable("latex",}
 \BaseNTok{          booktabs = T,}
@@
 
-\begin{longtable}[]{@{}cll@{}}
-\caption{\label{tab:unnamed-chunk-2}\label{tab:cooltable}Mean and
-Median}\tabularnewline
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-2}\label{tab:cooltable}Mean and Median}
+\centering
+\begin{tabular}[t]{cll}
 \toprule
-Supplement type & Median & Mean\tabularnewline
+Supplement type & Median & Mean\\
 \midrule
-\endfirsthead
+OJ & 22.7 & 20.66333\\
+VC & 16.5 & 16.96333\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{```\{r table2\}}
+\NormalTok{para = c("Intercept ($\textbackslash{}\textbackslash{}beta_0$)",}
+\BaseNTok{         "Parameter 1 ($\textbackslash{}\textbackslash{}beta_1$)",}
+\BaseNTok{         "Parameter 2 ($\textbackslash{}\textbackslash{}beta_2$)",}
+\BaseNTok{         "Hurdle probability ($\textbackslash{}\textbackslash{}theta$)")}
+
+\NormalTok{tab <- data.frame(}
+\BaseNTok{    Parameter = para,}
+\BaseNTok{    Estimate = c(1.6, 1.2, 6.2, 0.5),}
+\BaseNTok{    Error = c(0.41, 0.02, 0.09, 0.07),}
+\BaseNTok{    CI = c("[0.698, 2.477]",}
+\BaseNTok{           "[1.123, 1.235]",}
+\BaseNTok{           "[6.051, 6.423]",}
+\BaseNTok{           "[0.353, 0.644]"),}
+\BaseNTok{    Rhat = c(rep("1.00", 4)))}
+
+\NormalTok{kable(tab,}
+\BaseNTok{      "latex",}
+\BaseNTok{      align = "lcccc",}
+\BaseNTok{      booktabs = TRUE,}
+\BaseNTok{      escape = FALSE,}
+\BaseNTok{      caption = "\textbackslash{}\textbackslash{}label\{tab:mathtable\}A table with LaTeX Math symbols")}
+\NormalTok{```}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-3}\label{tab:mathtable}A table with LaTeX Math symbols}
+\centering
+\begin{tabular}[t]{lcccc}
 \toprule
-Supplement type & Median & Mean\tabularnewline
+Parameter & Estimate & Error & CI & Rhat\\
 \midrule
-\endhead
-OJ & 22.7 & 20.66333\tabularnewline
-VC & 16.5 & 16.96333\tabularnewline
+Intercept ($\beta_0$) & 1.6 & 0.41 & {}[0.698, 2.477] & 1.00\\
+Parameter 1 ($\beta_1$) & 1.2 & 0.02 & {}[1.123, 1.235] & 1.00\\
+Parameter 2 ($\beta_2$) & 6.2 & 0.09 & {}[6.051, 6.423] & 1.00\\
+Hurdle probability ($\theta$) & 0.5 & 0.07 & {}[0.353, 0.644] & 1.00\\
 \bottomrule
-\end{longtable}
+\end{tabular}
+\end{table}
 
@@
 \begin{longtable}[]{@{}cll@{}}
-\caption{\label{tab:unnamed-chunk-11}\label{tab:stable}This table
+\caption{\label{tab:unnamed-chunk-12}\label{tab:stable}This table
 again}\tabularnewline

### 2024-05-18 elsevier/cover_letter.Rmd
update `cover_letter.Rmd`
update `cover_letter.Rmd`: add long version for new submission

@@
 
-### New submission {-}
+### New submission - short version {-}
 Month Day, Year
@@
 I am happy to submit my manuscript, **article_name**, for your consideration at *journal_name*. 
-This work *do sth interesting*. 
+This work *did sth interesting*. 
 The main conclusion is that *sth cool*.
@@
 Professor
+
+### New submission - long version {-}
+Journal editor's name  
+Title  
+*Journal Name*
+
+Month Day, Year
+
+Dear Dr.[last_name],
+
+I would like to submit the manuscript entitled [**article_name**] by [author names] for consideration as [paper type: an original article / a brief communication / a case report / etc.] in [*Journal Name*].
+
+[Summarize the research problem/gap, your main research findings, and the implications of your findings]. 
+We believe these findings will be of interest to the readers of your journal.
+
+[[Revise or delete any of the following standard statements used in cover letter]]  
+We declare that this manuscript is original, has not been published before, and is not currently under consideration for publication elsewhere.
+
+We are unaware of any conflicts of interest associated with this publication, and there has been no significant financial support for this work that could have influenced its outcome. 
+As the Corresponding Author, I confirm that the manuscript has been read and approved for submission by all the named authors.
+
+[[Add any other statements/information required by the journal here]]
+
+We hope you find our manuscript suitable for publication and look forward to your response.
+
+Sincerely,
+
+[Corresponding Author's Name], PhD  
+Department Name, Institution Name  
+Postal Address  
+Tel./Fax: xxxxxx  
+Email: xxxxxx
 
